---
title: "Untitled"
author: "Rizal Mujahiddan"
date: "5/25/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  Nomor 1
## Generate Data Normal
```{r}
set.seed(1234)
data_100_1 <- rnorm(100,mean=10,sd=5)
data_100_1
```
## Boxplot
```{r}
boxplot(data_100_1,horizontal = TRUE,
        main="Boxplot Nomor 1")
```

## Summary
```{r}
summary(data_100_1)
```



#  Nomor 2
## Add Pencilan
```{r}
set.seed(1234)
data_100_2 <- c(data_100_1,30,35,40)
data_100_2
```

## Boxplot Nomor 2
```{r}
boxplot(data_100_2,horizontal=TRUE,
        main="Boxplot Nomor 2")
```
##
```{r}
summary(data_100_2)
```


#  Nomor 3
## Generate Data 
```{r}
set.seed(1234)
data_100_3 <- c(data_100_1,-30,-35,-40)
data_100_3
```

## Boxplot Nomor 3
```{r}
boxplot(data_100_3,
        horizontal = TRUE,
        main="Boxplot Nomor 3")
```

## Summary Nomor 3
```{r}
summary(data_100_3)
```

#  Nomor 4
## Generate data
```{r}
data_100_4 <- c(-30,-35,-40,data_100_1,30,35,40)
data_100_4
```
## boxplot
```{r}
boxplot(data_100_4,main="Boxplot Nomor 4",horizontal = TRUE)
```

## summary
```{r}
summary(data_100_4)
```

#  Nomor 5
## Generate data
```{r}
set.seed(1234)
data_10_5 <- rnorm(10,mean=10,sd=5)
data_10_5
```

## Boxplot
```{r}
boxplot(data_10_5,main="Boxplot Nomor 5",horizontal = TRUE)
```

## Summary
```{r}
summary(data_100_5)
```

#  Nomor 6
## Generate
```{r}
data_10_6 <- c(data_10_5,30,35)
data_10_6
```

## Boxplot
```{r}
boxplot(data_10_6,main="Boxplot Nomor 6",horizontal=TRUE)
```

## Summary
```{r}
summary(data_10_6)
```

# Nomor 7
## Generate data
```{r}
data_10_7 <- c(-30,-35,data_10_5)
data_10_7
```

## Boxplot
```{r}
boxplot(data_10_7,horizontal = TRUE,main="Boxplot Nomor 7")
```

## Summary
```{r}
summary(data_10_7)
```

#  Nomor 8
## Generate data
```{r}
data_10_8 <- c(-30,-35,data_10_5,30,35)
data_10_8
```

## Boxplot
```{r}
boxplot(data_10_8)
```

## Summary
```{r}
summary(data_10_8)
```


## imputation to missing value in data vector
### 100
```{r}
library(openxlsx)
panjangkolom_100 <- c(length(data_100_1),length(data_100_2),
                      length(data_100_3),length(data_100_4))
data_100_li <- list( data_100_1 = data_100_1,data_100_2 = data_100_2,
                  data_100_3 = data_100_3,data_100_4 = data_100_4)

max_panjangkolom_100 <- max(panjangkolom_100)

for(i in names(data_100_li)){
  if(length(data_100_li[[i]]) < max_panjangkolom_100){
    data_100_li[[i]] <- c(data_100_li[[i]] , 
                          rep(NA,max_panjangkolom_100 - length(data_100_li[[i]])))
  }
}

data_100 <- data.frame(data_100_li)
data_100
```

### 10
```{r}
library(openxlsx)
panjangkolom_10 <- c(length(data_10_5),length(data_10_6),
                      length(data_10_7),length(data_10_8))
data_10_li <- list(data_10_5 = data_10_5,data_10_6 = data_10_6,
                  data_10_7 = data_10_7,data_10_8 = data_10_8)

max_panjangkolom_10 <- max(panjangkolom_10)

for(i in names(data_10_li)){
  if(length(data_10_li[[i]]) < max_panjangkolom_10){
    data_10_li[[i]] <- c(data_10_li[[i]] ,
                         rep(NA,max_panjangkolom_10 - length(data_10_li[[i]])))
  }
}

data_10 <- data.frame(data_10_li)
data_10
```

## Writing xlsx file
```{r}
dataset_names <- list('Data_banyaknya_100' = data_100, 'Data_banyaknya_10' = data_10)
write.xlsx(dataset_names, file = 'G64190069_Rizal Mujahiddan.xlsx')
```

